Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-06-04 WSSSPE1_report/WSSSPE1_summary_report.tex
FastMATH is a packaging and configuring system for Math libs for HPC, removing it for now, looking to include it in a different place
fixing grammar

Some examples of such software discussed as part of the workshop are,
\toolname{DUNE (o.r. 2008)}, \toolname{R/qtl} (o.r. 2002), \toolname{Kitware} (o.r. 1998),
\toolname{PETSc} (o.r. 1995), \toolname{MINRES-QLP} (o.r. 2007), \toolname{FASTMath} (o.r. \textcolor{red}{TBD - Is FASTMath really a software project, or a collection of different packages?}).  Most of
the above efforts are focused on one scientific or applied
mathematics domain. However, sometimes such projects grow beyond the
initial vision of developers. One such example is \toolname{Kitware},
which while being a software product specializing in the scientific
process, has a core focus of developing communities around software
processes. Another instance of this process is the development of the
\toolname{CMake} build utility, which started out as a building tool
for \toolname{ITK} but grew to become a generic build utility for C++
projects. Similarly, \toolname{PETSc} is growing towards becoming a
general purpose utility system usable for solving a variety of
scientific problems.

>>>>

Some examples of such software discussed as part of the workshop are
\toolname{DUNE (o.r. 2008)}, \toolname{R/qtl} (o.r. 2002), \toolname{Kitware} (o.r. 1998),
\toolname{PETSc} (o.r. 1995), and \toolname{MINRES-QLP} (o.r. 2007),
%\toolname{FASTMath} (o.r. \textcolor{red}{TBD - Is FASTMath really a software project, or a collection of different packages?}).
most of which are focused on one scientific or applied
mathematics domain. However, sometimes such projects grow beyond the
initial vision of developers. One such example is \toolname{Kitware},
which while being a software product specializing in the scientific
process, has a core focus of developing communities around software
processes. Another instance of this process is the development of the
\toolname{CMake} build utility, which started out as a building tool
for \toolname{ITK} but grew to become a generic build utility for C++
projects. Similarly, \toolname{PETSc} is growing towards becoming a
general purpose utility system usable for solving a variety of
scientific problems.
